Incentivizing Exploration with Unbiased History

### 2018-11-02 main.tex
Added notation for constants in low-deviation assumption for agents' estimates.
Added a file for the intro.
Added a macro.
Added some macro.
define macro \NG for number of groups
a new macro
abstract added

@@

@@

\title{Incentivizing Exploration with Unbiased History}

@@

\thispagestyle{empty}
\begin{abstract}
aaa
\end{abstract}
\end{titlepage}

\input{model}

>>>>

% new notation for low-deviation assumption on agents' reward estimates
\newcommand{\estN}{N_{\term{est}}}
\newcommand{\estC}{C_{\term{est}}}

% notation for 3level section
\newcommand{\conf}[1]{\mathtt{conf}\left(#1\right)}
\newcommand{\event}[1]{\ensuremath{\mathtt{event}_{#1}}\xspace}

@@

%number of groups 
\def\NG{\sigma}

@@

%index on the tap
\def\z{z}
\title{Incentivizing Exploration with Unbiased History}

@@

\thispagestyle{empty}
\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.  A sequence of agents each choose an action with the goal of maximizing payoff given estimates of the state of the world.  A recommendation algorithm tries to coordinate the choices of the agents by sending messages about the history of past actions.  The goal of the algorithm is to minimize the regret of the action sequence.

In this paper, we study a particular class of recommendation algorithms that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.  One trivial message of this form contains the full history; a recommendation algorithm that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a recommendation algorithm using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}

\input{intro}
\input{model}
